---
title: "Diabetic Retinopathy Prediction"
author: "Nikesh Yadav"
date: "12/20/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


Load the libraries

```{r}
library(imager)
library(EBImage)
library(randomForest)
library(glmnet)
library(e1071)
```

Handy dandy function to extract the grayscale pixel values of resized images

```{r}
GSvals <- function(eye_Image) {
  im <- load.image(eye_Image)
  gray <- grayscale(im)
  resize.im <- resize(gray, w=100, h=100)
  mat <- matrix(resize.im, nrow=1)
  return(mat)
}
```


How does the diabetic eyes look?

```{r}
diabetic <- load.image("eyes/dr3.jpg")
plot(diabetic)
```

And the healthy eyes?

```{r}
healthy <- load.image("eyes/h15.jpg")
plot(healthy)
```

How the resized grayscale 100 * 100 image look?

```{r}
resiz <- resize(diabetic, w=100, h=100)
gr <- grayscale(resiz)
plot(gr)
```


Load pixel values for Diabetic Retinopathy eyes

```{r}
dr1 <- GSvals("eyes/dr1.jpg")
dr2 <- GSvals("eyes/dr2.jpg")
dr3 <- GSvals("eyes/dr3.jpg")
dr4 <- GSvals("eyes/dr4.jpg")
dr5 <- GSvals("eyes/dr5.jpg")
dr6 <- GSvals("eyes/dr6.jpg")
dr7 <- GSvals("eyes/dr7.jpg")
dr8 <- GSvals("eyes/dr8.jpg")
dr9 <- GSvals("eyes/dr9.jpg")
dr10 <- GSvals("eyes/dr10.jpg")
dr11 <- GSvals("eyes/dr11.jpg")
dr12 <- GSvals("eyes/dr12.jpg")
dr13 <- GSvals("eyes/dr13.jpg")
dr14 <- GSvals("eyes/dr14.jpg")
dr15 <- GSvals("eyes/dr15.jpg")
dr16 <- GSvals("eyes/dr16.jpg")
dr17 <- GSvals("eyes/dr17.jpg")
dr18 <- GSvals("eyes/dr18.jpg")
dr19 <- GSvals("eyes/dr19.jpg")
dr20 <- GSvals("eyes/dr20.jpg")
dr21 <- GSvals("eyes/dr21.jpg")
dr22 <- GSvals("eyes/dr22.jpg")
dr23 <- GSvals("eyes/dr23.jpg")
dr24 <- GSvals("eyes/dr24.jpg")
dr25 <- GSvals("eyes/dr25.jpg")
dr26 <- GSvals("eyes/dr29.jpg")
dr27 <- GSvals("eyes/dr27.jpg")
dr28 <- GSvals("eyes/dr28.jpg")
dr29 <- GSvals("eyes/dr29.jpg")
dr30 <- GSvals("eyes/dr30.jpg")
dr31 <- GSvals("eyes/dr31.jpg")
dr32 <- GSvals("eyes/dr32.jpg")
dr33 <- GSvals("eyes/dr33.jpg")
dr34 <- GSvals("eyes/dr34.jpg")
dr35 <- GSvals("eyes/dr35.jpg")
dr36 <- GSvals("eyes/dr36.jpg")
dr37 <- GSvals("eyes/dr37.jpg")
dr38 <- GSvals("eyes/dr38.jpg")
dr39 <- GSvals("eyes/dr39.jpg")
dr40 <- GSvals("eyes/dr40.jpg")
dr41 <- GSvals("eyes/dr41.jpg")
dr42 <- GSvals("eyes/dr42.jpg")
dr43 <- GSvals("eyes/dr43.jpg")
dr44 <- GSvals("eyes/dr44.jpg")
dr45 <- GSvals("eyes/dr45.jpg")
dr46 <- GSvals("eyes/dr46.jpg")
dr47 <- GSvals("eyes/dr47.jpg")
dr48 <- GSvals("eyes/dr48.jpg")
dr49 <- GSvals("eyes/dr49.jpg")
dr50 <- GSvals("eyes/dr50.jpg")
dr51 <- GSvals("eyes/dr51.jpg")
dr52 <- GSvals("eyes/dr52.jpg")
dr53 <- GSvals("eyes/dr53.jpg")
dr54 <- GSvals("eyes/dr54.jpg")
dr55 <- GSvals("eyes/dr55.jpg")
dr56 <- GSvals("eyes/dr56.jpg")
dr57 <- GSvals("eyes/dr57.jpg")
dr58 <- GSvals("eyes/dr58.jpg")
dr59 <- GSvals("eyes/dr59.jpg")
dr60 <- GSvals("eyes/dr60.jpg")
dr61 <- GSvals("eyes/dr61.jpg")
dr62 <- GSvals("eyes/dr62.jpg")
dr63 <- GSvals("eyes/dr63.jpg")
dr64 <- GSvals("eyes/dr64.jpg")
dr65 <- GSvals("eyes/dr65.jpg")
dr66 <- GSvals("eyes/dr66.jpg")
dr67 <- GSvals("eyes/dr67.jpg")
dr68 <- GSvals("eyes/dr68.jpg")
dr69 <- GSvals("eyes/dr69.jpg")
dr70 <- GSvals("eyes/dr70.jpg")
dr71 <- GSvals("eyes/dr71.jpg")
dr72 <- GSvals("eyes/dr72.jpg")
dr73 <- GSvals("eyes/dr73.jpg")
dr74 <- GSvals("eyes/dr74.jpg")
dr75 <- GSvals("eyes/dr75.jpg")
dr76 <- GSvals("eyes/dr76.jpg")
dr77 <- GSvals("eyes/dr77.jpg")
dr78 <- GSvals("eyes/dr78.jpg")
dr79 <- GSvals("eyes/dr79.jpg")
dr80<- GSvals("eyes/dr80.jpg")
dr81 <- GSvals("eyes/dr81.jpg")
dr82 <- GSvals("eyes/dr82.jpg")
dr83 <- GSvals("eyes/dr83.jpg")
dr84 <- GSvals("eyes/dr84.jpg")
dr85 <- GSvals("eyes/dr85.jpg")
dr86 <- GSvals("eyes/dr86.jpg")
dr87 <- GSvals("eyes/dr87.jpg")
dr88 <- GSvals("eyes/dr88.jpg")
dr89 <- GSvals("eyes/dr89.jpg")
```

Load the pixel values for healthy eyes

```{r}
h1 <- GSvals("eyes/h1.jpg")
h2 <- GSvals("eyes/h2.jpg")
h3 <- GSvals("eyes/h3.jpg")
h4 <- GSvals("eyes/h4.jpg")
h5 <- GSvals("eyes/h5.jpg")
h6 <- GSvals("eyes/h6.jpg")
h7 <- GSvals("eyes/h7.jpg")
h8 <- GSvals("eyes/h8.jpg")
h9 <- GSvals("eyes/h9.jpg")
h10 <- GSvals("eyes/h10.jpg")
h11 <- GSvals("eyes/h11.jpg")
h12 <- GSvals("eyes/h12.jpg")
h13 <- GSvals("eyes/h13.jpg")
h14 <- GSvals("eyes/h14.jpg")
h15 <- GSvals("eyes/h15.jpg")
h16 <- GSvals("eyes/h16.jpg")
h17 <- GSvals("eyes/h17.jpg")
h18 <- GSvals("eyes/h18.jpg")
h19 <- GSvals("eyes/h19.jpg")
h20 <- GSvals("eyes/h20.jpg")
h21 <- GSvals("eyes/h21.jpg")
h22 <- GSvals("eyes/h22.jpg")
h23 <- GSvals("eyes/h23.jpg")
h24 <- GSvals("eyes/h24.jpg")
h25 <- GSvals("eyes/h25.jpg")
h26 <- GSvals("eyes/h26.jpg")
h27 <- GSvals("eyes/h27.jpg")
h28 <- GSvals("eyes/h28.jpg")
h29 <- GSvals("eyes/h29.jpg")
h30 <- GSvals("eyes/h30.jpg")
h31 <- GSvals("eyes/h31.jpg")
h32 <- GSvals("eyes/h32.jpg")
h33 <- GSvals("eyes/h33.jpg")
h34 <- GSvals("eyes/h34.jpg")
h35 <- GSvals("eyes/h35.jpg")
h36 <- GSvals("eyes/h36.jpg")
h37 <- GSvals("eyes/h37.jpg")
h38 <- GSvals("eyes/h38.jpg")
h39 <- GSvals("eyes/h39.jpg")
h40 <- GSvals("eyes/h40.jpg")
```


Create a data frame eye.df where each row consists of pixel values of each image and a response variable. Assign the response variable as 1 for diabetic retinopathy and 0 for healthy eyes

```{r}
type = c(rep(1,89), rep(0,40))
eye.df <- data.frame(rbind(
  dr1,dr2,dr3,dr4,dr5,dr6,dr7,dr8,dr9,dr10,dr11,dr12,dr13,dr14,dr15,dr16,dr17,dr18,
  dr19,dr20,dr21,dr22,dr23,dr24,dr25,dr26,dr27,dr28,dr29,dr30,dr31,dr32,dr33,dr34,
  dr35,dr36,dr37,dr38,dr39,dr40,dr41,dr42,dr43,dr44,dr45,dr46,dr47,dr48,dr49,dr50,
  dr51,dr52,dr53,dr54,dr55,dr56,dr57,dr58,dr59,dr60,dr61,dr62,dr63,dr64,dr65,dr66,
  dr67,dr68,dr69,dr70,dr71,dr72,dr73,dr74,dr75,dr76,dr77,dr78,dr79,dr80,dr81,dr82,
  dr83,dr84,dr85,dr86,dr87,dr88,dr89,h1,h2,h3,h4,h5,h6,h7,h8,h9,h10,h11,h12,h13,h14,
  h15,h16,h17,h18,h19,h20,h21,h22,h23,h24,h25,h26,h27,h28,h29,h30,h31,h32,h33,h34,
  h35,h36,h37,h38,h39,h40), 
                     
  resp=type)
```

Take principal components of newly created eye.df that has 10,000 predictors

```{r}
eye.df_noresp <- eye.df[,-ncol(eye.df)]
pca.eye <- prcomp(eye.df_noresp, scale=T)
summary(pca.eye) 

#The rotation matrix
rots <- pca.eye$rotation 
dim(rots) 
eye.mat <- as.matrix(eye.df_noresp[,1:ncol(eye.df_noresp)]) 
dim(eye.mat) 

#Principal components
pcs <- eye.mat %*% rots
dim(pcs) 

#Data frame with principal components as predictors and the corresponding response variable
prcomp.df <- data.frame(pcs, resp = type)
```

Try RandomForest on the principal components

```{r}
nr <- nrow(prcomp.df)
test <- sample(1:nr, nr/2, rep=F)
train <- setdiff(1:nr, test)

test.df <- prcomp.df[test,]
train.df <- prcomp.df[train,]

rf <- randomForest(as.factor(resp)~., data=train.df, ntree=500)
pred <- predict(rf, newdata = test.df)
pred
test.df$resp
mean(pred != test.df$resp)
```

Now let's try LASSO on 10,000 predictors with lambda from 10^-2 - 10^2 divided into 100 sequences

```{r}
x <- data.matrix(eye.df[,-ncol(eye.df)])
y <- data.matrix(eye.df[,ncol(eye.df)])
test <- sample(1:nr, nr/2, rep=F)
train <- setdiff(1:nr, test)
x.train <- x[train,]
y.train <- y[train,]
x.test <- x[test,]
y.test <- y[test,]

cv.lasso <- cv.glmnet(x.train, y.train, alpha = 1, family="binomial")
cv.lasso$lambda.min
cv.lasso$lambda.1se

error <- rep(0,100)
i <- 1
for (lamb in 10^seq(-2,2, length = 100)) {
  test <- sample(1:nr, nr/2, rep=F)
  train <- setdiff(1:nr, test)
  x.train <- x[train,]
  y.train <- y[train,]
  x.test <- x[test,]
  y.test <- y[test,]
  fit.lasso <- glmnet(x.train, y.train, alpha = 1, lambda = lamb, family = "binomial")
  pred.lasso <- predict(fit.lasso, newx = x.test, type="class")
  error[i] = mean(as.numeric(pred.lasso) != y.test)
  i <- i+1
} 
print(error)
min(error)
```

How does it look for lambda values in between cv.lasso$lambda.min and cv.lasso$lambda.1se

```{r}
i <- 1
for (lamb in seq(cv.lasso$lambda.min, cv.lasso$lambda.1se, length=100)) {
  test <- sample(1:nr, nr/2, rep=F)
  train <- setdiff(1:nr, test)
  x.train <- x[train,]
  y.train <- y[train,]
  x.test <- x[test,]
  y.test <- y[test,]
  fit.lasso <- glmnet(x.train, y.train, alpha = 1, lambda = lamb, family = "binomial")
  pred.lasso <- predict(fit.lasso, newx = x.test, type="class")
  error[i] = mean(as.numeric(pred.lasso) != y.test)
  i <- i+1
} 
print(error)
min(error)
```

How does the LASSO model look?

```{r}
fit.lasso <- glmnet(x.train, y.train, alpha=1, lambda = cv.lasso$lambda.min, family="binomial")
coef(fit.lasso) 
```

Lasso on Principal Components

```{r}
x <- data.matrix(prcomp.df[,-ncol(prcomp.df)])
y <- data.matrix(prcomp.df[,ncol(prcomp.df)])
test <- sample(1:nr, nr/2, rep=F)
train <- setdiff(1:nr, test)
x.train <- x[train,]
y.train <- y[train,]
x.test <- x[test,]
y.test <- y[test,]

cv.lasso <- cv.glmnet(x.train, y.train, alpha = 1, family="binomial")
cv.lasso$lambda.min
cv.lasso$lambda.1se

error <- rep(0,100)
i <- 1
for (lamb in seq(cv.lasso$lambda.min, cv.lasso$lambda.1se, length=100)) {
  test <- sample(1:nr, nr/2, rep=F)
  train <- setdiff(1:nr, test)
  x.train <- x[train,]
  y.train <- y[train,]
  x.test <- x[test,]
  y.test <- y[test,]
  fit.lasso <- glmnet(x.train, y.train, alpha = 1, lambda = lamb, family = "binomial")
  pred.lasso <- predict(fit.lasso, newx = x.test, type="class")
  error[i] = mean(as.numeric(pred.lasso) != y.test)
  i <- i+1
}
error
min(error)
```

Ridge Regression on Principal Components

```{r}
x <- data.matrix(prcomp.df[,-ncol(prcomp.df)])
y <- data.matrix(prcomp.df[,ncol(prcomp.df)])
test <- sample(1:nr, nr/2, rep=F)
train <- setdiff(1:nr, test)
x.train <- x[train,]
y.train <- y[train,]
x.test <- x[test,]
y.test <- y[test,]

cv.ridge <- cv.glmnet(x.train, y.train, alpha = 0, family="binomial")
cv.ridge$lambda.min
cv.ridge$lambda.1se

error <- rep(0,100)
i <- 1
for (lamb in seq(cv.ridge$lambda.min,cv.ridge$lambda.1se,length = 100)) {
  test <- sample(1:nr, nr/2, rep=F)
  train <- setdiff(1:nr, test)
  x.train <- x[train,]
  y.train <- y[train,]
  x.test <- x[test,]
  y.test <- y[test,]
  fit.ridge <- glmnet(x.train, y.train, alpha = 0, lambda = lamb, family = "binomial")
  pred.ridge <- predict(fit.ridge, newx = x.test, type="class")
  error[i] = mean(as.numeric(pred.ridge) != y.test)
  i <- i+1
}
error
min(error)
```

SVM on Principal Components with Radial kernel

```{r}
test <- sample(1:nr, nr/2, rep=F)
train <- setdiff(1:nr, test)
test.df <- prcomp.df[test,]
train.df <- prcomp.df[train,]

tune.svm <-
  tune(svm,as.factor(resp) ~.,
       data=train.df,
       kernel="radial",
       scale=F,
       ranges=list(cost=10^seq(-5,5,length=50), gamma=10^seq(-5,5)),
       ##use cross=3 to speed up
       tunecontrol=tune.control(cross=3))

C <- tune.svm$best.parameters[1]
G <- tune.svm$best.parameters[2]
C
G

svmfit <- svm(as.factor(resp) ~., 
              data = train.df,
              kernel = "radial",
              cost = C,
              gamma = G,
              scale = F)
pred.svm <- predict(svmfit, newdata = test.df)
pred.svm
test.df$resp
mean(pred.svm != test.df$resp)

```

SVM with Polynomial kernel

```{r}
test <- sample(1:nr, nr/2, rep=F)
train <- setdiff(1:nr, test)
test.df <- prcomp.df[test,]
train.df <- prcomp.df[train,]

tune.svm <-
  tune(svm,as.factor(resp) ~.,
       data=train.df,
       kernel="polynomial",
       scale=F,
       ranges=list(cost=10^seq(-10,10,length=50), d=seq(1,10)),
       ##use cross=3 to speed up
       tunecontrol=tune.control(cross=3))

C <- tune.svm$best.parameters[1]
D <- tune.svm$best.parameters[2]
C
D

svmfit <- svm(as.factor(resp) ~., 
              data = train.df,
              kernel = "polynomial",
              cost = C,
              degree = D,
              scale = F)
pred.svm <- predict(svmfit, newdata = test.df)
pred.svm
test.df$resp
mean(pred.svm != test.df$resp)
```


#Now let's resize the images to 10 * 10 !!

How will the image look when resize to 10 * 10?

```{r}
resiz <- resize(diabetic, w=10, h=10)
gr <- grayscale(resiz)
plot(gr)
```


Do same things done above

```{r}
GSvals <- function(eye_Image) {
  im <- load.image(eye_Image)
  gray <- grayscale(im)
  resize.im <- resize(gray, w=10, h=10)
  mat <- matrix(resize.im, nrow=1)
  return(mat)
}

#Diabetic Retinopathy
dr1 <- GSvals("eyes/dr1.jpg")
dr2 <- GSvals("eyes/dr2.jpg")
dr3 <- GSvals("eyes/dr3.jpg")
dr4 <- GSvals("eyes/dr4.jpg")
dr5 <- GSvals("eyes/dr5.jpg")
dr6 <- GSvals("eyes/dr6.jpg")
dr7 <- GSvals("eyes/dr7.jpg")
dr8 <- GSvals("eyes/dr8.jpg")
dr9 <- GSvals("eyes/dr9.jpg")
dr10 <- GSvals("eyes/dr10.jpg")
dr11 <- GSvals("eyes/dr11.jpg")
dr12 <- GSvals("eyes/dr12.jpg")
dr13 <- GSvals("eyes/dr13.jpg")
dr14 <- GSvals("eyes/dr14.jpg")
dr15 <- GSvals("eyes/dr15.jpg")
dr16 <- GSvals("eyes/dr16.jpg")
dr17 <- GSvals("eyes/dr17.jpg")
dr18 <- GSvals("eyes/dr18.jpg")
dr19 <- GSvals("eyes/dr19.jpg")
dr20 <- GSvals("eyes/dr20.jpg")
dr21 <- GSvals("eyes/dr21.jpg")
dr22 <- GSvals("eyes/dr22.jpg")
dr23 <- GSvals("eyes/dr23.jpg")
dr24 <- GSvals("eyes/dr24.jpg")
dr25 <- GSvals("eyes/dr25.jpg")
dr26 <- GSvals("eyes/dr29.jpg")
dr27 <- GSvals("eyes/dr27.jpg")
dr28 <- GSvals("eyes/dr28.jpg")
dr29 <- GSvals("eyes/dr29.jpg")
dr30 <- GSvals("eyes/dr30.jpg")
dr31 <- GSvals("eyes/dr31.jpg")
dr32 <- GSvals("eyes/dr32.jpg")
dr33 <- GSvals("eyes/dr33.jpg")
dr34 <- GSvals("eyes/dr34.jpg")
dr35 <- GSvals("eyes/dr35.jpg")
dr36 <- GSvals("eyes/dr36.jpg")
dr37 <- GSvals("eyes/dr37.jpg")
dr38 <- GSvals("eyes/dr38.jpg")
dr39 <- GSvals("eyes/dr39.jpg")
dr40 <- GSvals("eyes/dr40.jpg")
dr41 <- GSvals("eyes/dr41.jpg")
dr42 <- GSvals("eyes/dr42.jpg")
dr43 <- GSvals("eyes/dr43.jpg")
dr44 <- GSvals("eyes/dr44.jpg")
dr45 <- GSvals("eyes/dr45.jpg")
dr46 <- GSvals("eyes/dr46.jpg")
dr47 <- GSvals("eyes/dr47.jpg")
dr48 <- GSvals("eyes/dr48.jpg")
dr49 <- GSvals("eyes/dr49.jpg")
dr50 <- GSvals("eyes/dr50.jpg")
dr51 <- GSvals("eyes/dr51.jpg")
dr52 <- GSvals("eyes/dr52.jpg")
dr53 <- GSvals("eyes/dr53.jpg")
dr54 <- GSvals("eyes/dr54.jpg")
dr55 <- GSvals("eyes/dr55.jpg")
dr56 <- GSvals("eyes/dr56.jpg")
dr57 <- GSvals("eyes/dr57.jpg")
dr58 <- GSvals("eyes/dr58.jpg")
dr59 <- GSvals("eyes/dr59.jpg")
dr60 <- GSvals("eyes/dr60.jpg")
dr61 <- GSvals("eyes/dr61.jpg")
dr62 <- GSvals("eyes/dr62.jpg")
dr63 <- GSvals("eyes/dr63.jpg")
dr64 <- GSvals("eyes/dr64.jpg")
dr65 <- GSvals("eyes/dr65.jpg")
dr66 <- GSvals("eyes/dr66.jpg")
dr67 <- GSvals("eyes/dr67.jpg")
dr68 <- GSvals("eyes/dr68.jpg")
dr69 <- GSvals("eyes/dr69.jpg")
dr70 <- GSvals("eyes/dr70.jpg")
dr71 <- GSvals("eyes/dr71.jpg")
dr72 <- GSvals("eyes/dr72.jpg")
dr73 <- GSvals("eyes/dr73.jpg")
dr74 <- GSvals("eyes/dr74.jpg")
dr75 <- GSvals("eyes/dr75.jpg")
dr76 <- GSvals("eyes/dr76.jpg")
dr77 <- GSvals("eyes/dr77.jpg")
dr78 <- GSvals("eyes/dr78.jpg")
dr79 <- GSvals("eyes/dr79.jpg")
dr80<- GSvals("eyes/dr80.jpg")
dr81 <- GSvals("eyes/dr81.jpg")
dr82 <- GSvals("eyes/dr82.jpg")
dr83 <- GSvals("eyes/dr83.jpg")
dr84 <- GSvals("eyes/dr84.jpg")
dr85 <- GSvals("eyes/dr85.jpg")
dr86 <- GSvals("eyes/dr86.jpg")
dr87 <- GSvals("eyes/dr87.jpg")
dr88 <- GSvals("eyes/dr88.jpg")
dr89 <- GSvals("eyes/dr89.jpg")


#Healthy Eyes
h1 <- GSvals("eyes/h1.jpg")
h2 <- GSvals("eyes/h2.jpg")
h3 <- GSvals("eyes/h3.jpg")
h4 <- GSvals("eyes/h4.jpg")
h5 <- GSvals("eyes/h5.jpg")
h6 <- GSvals("eyes/h6.jpg")
h7 <- GSvals("eyes/h7.jpg")
h8 <- GSvals("eyes/h8.jpg")
h9 <- GSvals("eyes/h9.jpg")
h10 <- GSvals("eyes/h10.jpg")
h11 <- GSvals("eyes/h11.jpg")
h12 <- GSvals("eyes/h12.jpg")
h13 <- GSvals("eyes/h13.jpg")
h14 <- GSvals("eyes/h14.jpg")
h15 <- GSvals("eyes/h15.jpg")
h16 <- GSvals("eyes/h16.jpg")
h17 <- GSvals("eyes/h17.jpg")
h18 <- GSvals("eyes/h18.jpg")
h19 <- GSvals("eyes/h19.jpg")
h20 <- GSvals("eyes/h20.jpg")
h21 <- GSvals("eyes/h21.jpg")
h22 <- GSvals("eyes/h22.jpg")
h23 <- GSvals("eyes/h23.jpg")
h24 <- GSvals("eyes/h24.jpg")
h25 <- GSvals("eyes/h25.jpg")
h26 <- GSvals("eyes/h26.jpg")
h27 <- GSvals("eyes/h27.jpg")
h28 <- GSvals("eyes/h28.jpg")
h29 <- GSvals("eyes/h29.jpg")
h30 <- GSvals("eyes/h30.jpg")
h31 <- GSvals("eyes/h31.jpg")
h32 <- GSvals("eyes/h32.jpg")
h33 <- GSvals("eyes/h33.jpg")
h34 <- GSvals("eyes/h34.jpg")
h35 <- GSvals("eyes/h35.jpg")
h36 <- GSvals("eyes/h36.jpg")
h37 <- GSvals("eyes/h37.jpg")
h38 <- GSvals("eyes/h38.jpg")
h39 <- GSvals("eyes/h39.jpg")
h40 <- GSvals("eyes/h40.jpg")


### Assign 1 for Diabetic Retinopathy and 0 for Healthy eyes
type = c(rep(1,89), rep(0,40))
eye.df <- data.frame(rbind(
  dr1,dr2,dr3,dr4,dr5,dr6,dr7,dr8,dr9,dr10,dr11,dr12,dr13,dr14,dr15,dr16,dr17,dr18,
  dr19,dr20,dr21,dr22,dr23,dr24,dr25,dr26,dr27,dr28,dr29,dr30,dr31,dr32,dr33,dr34,
  dr35,dr36,dr37,dr38,dr39,dr40,dr41,dr42,dr43,dr44,dr45,dr46,dr47,dr48,dr49,dr50,
  dr51,dr52,dr53,dr54,dr55,dr56,dr57,dr58,dr59,dr60,dr61,dr62,dr63,dr64,dr65,dr66,
  dr67,dr68,dr69,dr70,dr71,dr72,dr73,dr74,dr75,dr76,dr77,dr78,dr79,dr80,dr81,dr82,
  dr83,dr84,dr85,dr86,dr87,dr88,dr89,h1,h2,h3,h4,h5,h6,h7,h8,h9,h10,h11,h12,h13,h14,
  h15,h16,h17,h18,h19,h20,h21,h22,h23,h24,h25,h26,h27,h28,h29,h30,h31,h32,h33,h34,
  h35,h36,h37,h38,h39,h40), 
  
  resp=type)
```

Take principal components of 100 predictors

```{r}
eye.df_noresp <- eye.df[,-ncol(eye.df)]
pca.eye <- prcomp(eye.df_noresp, scale=T)
summary(pca.eye) 
biplot(pca.eye)
rots <- pca.eye$rotation 
dim(rots) 
eye.mat <- as.matrix(eye.df_noresp[,1:ncol(eye.df_noresp)]) 
dim(eye.mat) 
pcs <- eye.mat %*% rots
dim(pcs) 
prcomp.df <- data.frame(pcs, resp = type)

```

LASSO on 100 predictors

```{r}
x <- data.matrix(eye.df[,-ncol(eye.df)])
y <- data.matrix(eye.df[,ncol(eye.df)])
test <- sample(1:nr, nr/2, rep=F)
train <- setdiff(1:nr, test)
x.train <- x[train,]
y.train <- y[train,]
x.test <- x[test,]
y.test <- y[test,]

cv.lasso <- cv.glmnet(x.train, y.train, alpha = 1, family="binomial")
cv.lasso$lambda.min

fit.lasso <- glmnet(x.train, y.train, alpha = 1, lambda = cv.lasso$lambda.min, family = "binomial")
coef(fit.lasso)
pred.lasso <- predict(fit.lasso, newx = x.test, type="class")
print(as.numeric(pred.lasso))
print(y.test)
mean(as.numeric(pred.lasso) != y.test)
```